### 2014-10-29 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL ECS: minor update to writeup

\begin{tabbing}
\hspace{1.5in} \= \\
ECS \> Emisssion Control System \\
HRR \> Heat Release Rate \\
NFRL \> National Fire Research Laboratory \\
NIST \> National Institute of Standards and Technology \\
PVC \> Polyvinyl Chlorine \\
\end{tabbing}

@@

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
ECS \> Emisssions Control System \\
HRR \> Heat Release Rate \\
NFRL \> National Fire Research Laboratory \\
NIST \> National Institute of Standards and Technology \\
PVC \> Polyvinyl Chlorine \\
\end{tabbing}

@@

\chapter{Emissions Control System}
\label{ecs}
The emissions control system for the NFRL is a combination spray dryer and pulse jet fabric filter system. The purpose is to remove both particulates and polluntants produced from experiments within the laboratory.
